\documentclass[a4paper]{article}
\usepackage[top=0.5cm,bottom=0.5cm,left=1cm,right=1cm]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}

\begin{document}
\title{Effectiveness of Public Transportation Across Cities}
\author{Rohit Kumar, PID - A53238243\\ Himanshu Gupta, PID-A53281369\\Rajat Sethi, PID-A53285419\\ Mingkun Yin, PID-A53273637}
\maketitle

\section{Problem}
Analysing the effectiveness of public transportation networks across cities in USA, Asia, and Europe. Across various parameters like, reduction in commuting time, cost effectiveness, reduction is emissions, reduction in road accidents.
\section{Dataset}
Publicly available datasets from American Public Transportation Association, Federal Transit Administration, and the Bureau of Transport Statistics.
\begin{itemize}
    \item \href{https://www.apta.com/resources/statistics/Documents/Forms/AllItems.aspx?&&p_SortBehavior=0&p_FileLeafRef=2014-APTA-Fact-Book-Appendix-B%2exls&&RootFolder=%2fresources%2fstatistics%2fDocuments%2fFactBook&PageFirstRow=1&TreeField=Folders&TreeValue=FactBook&ProcessQStringToCAML=1&&View={85AC02CD-F1C7-465B-976B-D192D673D93B}&InitialTabId=Ribbon%2EDocument&VisibilityContext=WSSTabPersistence}{APTA dataset} 
    \item \href{https://www.transit.dot.gov/ntd/ntd-data}{Federal Transit Administration dataset}
    \item \href{https://www.bts.gov/}{Bureau of Transport Statistics dataset}
\end{itemize}

\section{Proposed Solution and Real World Application}
There are multiple modes of transportation available in various cities, like the New York City Subway and the Muni Metro in San Francisco. We seek to measure the impact of public transport in the following terms:
\begin{itemize}
    \item Cost effectiveness from the perspective of city planners and users.
    \item Reduction in travel time.
    \item Reduction in road accidents/other casualties.
    \item Reduction in emissions.
    \item Effect on traffic congestions.
    \item Effect on car sales.
    \item Effect on the overall economy of the city.
    
\end{itemize}
\section{Project Steps}
\begin{center}
\begin{tabular}{|l|l|l|}
    \hline
Steps & Estimated Completion & Persons in charge \\
\hline
1. Data extraction and processing & One week & Rajat, Rohit, Himanshu, Mingkun \\
2. Data analysis and statistical modelling & Two weeks & Mingkun, Himanshu, Rohit, Rajat \\
3. Data visualization & One weeks & Rohit, Mingkun, Rajat, Himanshu\\
\hline
\end{tabular}
\end{center}

\section{Github Repo}
\href{https://github.com/rohit1347/ece143_g3}{Link}

\end{document}